Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers

### 2016-10-29 notes/poster/poster.tex
Incremental edits to the poster.

%%%%%%%%%%%%%%%
% Performance %
%%%%%%%%%%%%%%%
\section{Performance}
The Kinetisense sensor was used for the algorithm performance analysis in this paper.
This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
A separate instance of walking data was used specifically for training the classifier.

\begin{figure}[!ht]
\centering
\subfigure[Jogging]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
\subfigure[Bicycling]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
\caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced at decimation 8. Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectively.}
  \label{fig:MF_performance}
\end{figure}

Figures \ref{fig:frac_walking_jogging} and \ref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
As we would expect, the walking data reference matches better to walking data than to the other activities. The tail in figure \ref{fig:frac_walking_jogging} is attributed to brief moments of walking that was recorded during the jogging data collection.
ROC curves were produced from these corresponding results in figures \ref{fig:roc_walking_jogging} and \ref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from our classifier for bicycling.

>>>>

%%%%%%%%%%%%%%%
% Performance %
%%%%%%%%%%%%%%%
\section{Performance}
The Kinetisense sensor was used for the algorithm performance analysis.
This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
A separate instance of walking data was used specifically for training the classifier.

\begin{figure}[!ht]
\centering
\subfigure[\label{fig:frac_walking_jogging} Jogging]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
\subfigure[\label{fig:frac_walking_bicycling} Bicycling]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
\caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced at decimation 8.}
  \label{fig:MF_performance}
\end{figure}

Figures \ref{fig:frac_walking_jogging} and \ref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
